\boldmath Disconnected pseudo-$C_\ell$ covariances for projected large-scale structure data

### 2019-06-24 draft/paper.tex
Appendix A: comma + Fig -> Figure

    \begin{figure}
      \centering
      \includegraphics[width=\textwidth]{./figures/run_chi2_TT_TE_EE_TB_EB_BB.pdf}
      \caption{Same as Figure \ref{fig:chi2_1bin} for flat-sky fields. This
        figure additionally shows the $\chi^2$ distributions for power spectra
        involving $B$-modes. For the smaller scales covered by these flat-sky
        simulations, the NKA and spin-0 estimators work remarkably well, even
        for $B$-mode spectra. The distribution mean shift and width difference
        is of about $\lesssim 2\%$ for all cases.}
      \label{fig:chi2_1bin_flat}
    \end{figure}
    We have repeated the analysis described in Section \ref{sec:results} on flat-sky realizations, making use of the flat-sky implementation of {\tt NaMaster}. We generate Gaussian realizations of the galaxy overdensity and shear maps making use of flat-sky extensions of the methods described in Section \ref{ssec:results.sims}. In this case we use a high-resolution mask constructed from the bright-object mask distributed with the first data release of the HSC collaboration \cite{2018PASJ...70S...4A} for the VVDS field, which is shown in Fig. \ref{fig:mask_flat}.

    We find similar levels of accuracy in the NKA and spin-0 estimators compared to the curved-sky case. The higher resolution and smaller area of these simulations allow us to focus on the small-scale galaxy clustering and lensing power spectra, covering the range of multipoles $\ell\in(120,17640)$ in constant bandpowers of width $\Delta \ell=240$. On these small scales, the shear power spectrum is more dominated by noise (e.g. see Fig. \ref{fig:cl-2bins}), and therefore there is roughly the same power in $E$ and $B$ modes. This reduces the sensitivity of the method to an inaccurate treatment of $E/B$ leakage, and the agreement between the sample covariance matrix and the NKA estimator improves significantly. This can be seen in Fig. \ref{fig:chi2_1bin_flat}, which shows the $\chi^2$ distributions for all possible power spectra (including those including $B$ modes) in the case of a single redshift bin. In all cases we find a good agreement between the $\chi^2$ distributions derived from all covariance matrix estimates (sample covariance, NKA and spin-0 in blue, orange and green respectively), which also accurately follow the expected $\chi^2$ distribution for the corresponding number of degrees of freedom (red dashed line).

>>>>

    \begin{figure}
      \centering
      \includegraphics[width=\textwidth]{./figures/run_chi2_TT_TE_EE_TB_EB_BB.pdf}
      \caption{Same as Figure \ref{fig:chi2_1bin} for flat-sky fields. This
        figure additionally shows the $\chi^2$ distributions for power spectra
        involving $B$-modes. For the smaller scales covered by these flat-sky
        simulations, the NKA and spin-0 estimators work remarkably well, even
        for $B$-mode spectra. The distribution mean shift and width difference
        is of about $\lesssim 2\%$ for all cases.}
      \label{fig:chi2_1bin_flat}
    \end{figure}
    We have repeated the analysis described in Section \ref{sec:results} on
    flat-sky realizations, making use of the flat-sky implementation of {\tt
      NaMaster}. We generate Gaussian realizations of the galaxy overdensity
    and shear maps making use of flat-sky extensions of the methods described
    in Section \ref{ssec:results.sims}. In this case we use a high-resolution
    mask constructed from the bright-object mask distributed with the first
    data release of the HSC collaboration \cite{2018PASJ...70S...4A} for the
    VVDS field, which is shown in Figure~\ref{fig:mask_flat}.

    We find similar levels of accuracy in the NKA and spin-0 estimators
    compared to the curved-sky case. The higher resolution and smaller area of
    these simulations allow us to focus on the small-scale galaxy clustering
    and lensing power spectra, covering the range of multipoles
    $\ell\in(120,17640)$ in constant bandpowers of width $\Delta \ell=240$. On
    these small scales, the shear power spectrum is more dominated by noise
    (e.g. see Fig. \ref{fig:cl-2bins}), and therefore there is roughly the
    same power in $E$ and $B$ modes. This reduces the sensitivity of the
    method to an inaccurate treatment of $E/B$ leakage, and the agreement
    between the sample covariance matrix and the NKA estimator improves
    significantly. This can be seen in Figure~\ref{fig:chi2_1bin_flat}, which shows the $\chi^2$ distributions for all possible power spectra (including those including $B$ modes) in the case of a single redshift bin. In all cases we find a good agreement between the $\chi^2$ distributions derived from all covariance matrix estimates (sample covariance, NKA and spin-0 in blue, orange and green respectively), which also accurately follow the expected $\chi^2$ distribution for the corresponding number of degrees of freedom (red dashed line).
